\newgeometry{top=1.3in,bottom=1.0in,left=1.5in,right=1.0in}
\doublespacing
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\pagenumbering{roman}
\newpage
\thispagestyle{empty}
\mbox{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
%\thispagestyle{empty}

\begin{center}
\textbf{\Large{Acknowledgements}}
\addcontentsline{toc}{section}{Acknowledgements}
\bigskip
\bigskip
\end{center}

The work presented in this thesis would not have been possible without the assistance
of countless individuals.  I extend my eternal gratitude  to all those people. However, despite being a dangerous practice, I would like to single out a few, select, individuals for special recognition.

 This thesis would not have seen the light of the day without the continuous and persistent motivation of my guide Prof. S. K. Saha. His advice and guidance  on technical  issues helped give direction to this research. Moreover, he played a pivotal role in providing the much needed psychological and emotional support. Each and every meeting with him was a booster to my self confidence. 
 
    
I am deeply grateful to my co-supervisor, Professor S. Bhasin in the Department of Electric Engineering at  IIT-Delhi, for his continued encouragement and invaluable suggestions in the field of control engineering and in particular adaptive control during this work. He has been instrumental in introducing me to the latest research results  in the field of time delayed non-linear systems.  
I also express my gratitude to Dr. Deepak N Badodkar, my supervisor at my parent organization BARC, Mumbai for his encouragement and the logistic support he had provided throughout the tenure of my research. Without his support the development and fabrication  of the  physical system would not have been possible.  


It will be imprudent not to mention the help and support provided by my colleague Shri. Rahul V Sakrikar. One person, on whom I fell back in case of any hardware issues be it electrical or mechanical. While discussing and sorting out technical glitches I found his profound experience and field knowledge highly enriching. I still remember his \textit{encouragin}g words, ``Are tera PhD ka kya hua? Saha kuch kaam nahi deya kya?" Another colleague, Shri Shishir Kr. Singh has provided his selfless service to help me develop all the software required for running the actual system. Without his help and support it would have been impossible to conduct experimental runs and data collection. I express my deepest regards to both of them.

I cannot forget the support and help of my co-researchers and classmates Dr. Riby Abraham, Dr. Parmanand Nandihal, Dr. Abdullah Aamir Hayat and Dr. Arun Dayal Uday during my stay and course work at IIT-Delhi. Thereafter, providing all kinds of logistic support at IIT-Delhi. Without their help it would have been impossible to continue my work at IIT-Delhi. I thank them from the bottom of my heart and wish them grand success  in their life.


Finally, I thank my two daughters, Akaisha and Sayuri, my mother for their patience  and support. Special thanks to my wife Namrata, who had taken upon herself  the responsibility of managing the family during my course work at IIT-Delhi and providing the required time and space for my research work thereafter. In absence of  her support, patience and companionship this journey would not have been completed.  



\bigskip
\bigskip
\bigskip
\bigskip

\hfill \textbf{Amaren Pasanna Das}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\restoregeometry
